Information Disclosure in Dynamic Innovation Contests

### 2025-05-22 paper/Paper.tex
update
update-paper
paper-update

@@

\subsection{Mapping the Model to the Data}

@@

3.

@@

relation between $\lambda$ and the proportion of data release?

@@

\section{Solve $S_t$ in Equation (\ref{filtered-S})}\label{app-S-equ}

@@

>>>>

\subsection{Out of Sample Performance}

@@

\subsection{Mapping the Model to the Real Data}

@@

3. How to select contests?

@@

To Do 1: relation between $\lambda$ and the proportion of data release?

By the data generating process (\ref{eq-leaderboard-gap}), we have a simple maximum likelihood estimation (MLE) of the true value of $\lambda$. 
Since $\hat{y}_t - y_t \sim \mathcal{N}(0, 1/(\lambda\Delta))$, we have 
\begin{equation*}
\lambda^{\text{MLE}} = \frac{n}{\Delta\sum^n_{i=1}(y_i - \hat{y}_i)^2}
\end{equation*}

To Do 2: validate the estimation of $\sigma$?

First, we estimate submission intensities $\tau_i(t)$ and $\tau_j(t)$ by kernel density estimation (KDE). 
Having $\hat{\tau}_i$ and $\hat{\tau}_j$, the effort levels of the two players are simply $m_i(t) = \hat{\tau}_i / r$ and $m_j(t) = \hat{\tau}_j / r$ by (\ref{eq-model-intensity}), where $r$ is the ratio of effort level and submission intensity. 
Next, with the submission times denoted by $\{t_k\}$, we have $y_{t_{k+1}} - y_{t_k} \sim \mathcal{N}\left(\frac{1}{r}\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds, \sigma^2(t_{k+1}-t_k)\right)$ by the dynamic of private leaderboard (\ref{eq-state-dynamics}). 
Then, by (\ref{normal-mle-r}) and (\ref{normal-mle-sigma}), we can estimate the parameters $r$ and $\sigma^2$ using MLE, that is  
\begin{equation*}
r^{\text{MLE}} = \frac{\sum_k\left[\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds\right]^2/(t_{k+1}-t_k)}{\sum_k(y_{t_{k+1}}-y_{t_k})\left[\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds\right] / (t_{k+1}-t_k)}
\end{equation*}
\begin{equation*}
\sigma^{\text{MLE}} = \frac{1}{n}\sum_k\frac{\left[y_{t_{k+1}}-y_{t_k}-\frac{1}{\hat{r}}\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds\right]^2}{t_{k+1}-t_k}
\end{equation*}

@@

\section{Auxiliary Results}

\subsection{Solve $S_t$ in Equation (\ref{filtered-S})}\label{app-S-equ}

@@

\subsection{MLE for Normal Distribution}

Suppose we observe independent data points \( X_1, ..., X_n \), where each \( X_k \sim \mathcal{N}(M_k / r, \sigma^2 T_k) \) with known constants \( M_k \) and \( T_k \). 
The goal is to estimate the parameters \( r \) and \( \sigma \) via maximum likelihood estimation (MLE).
Ignoring constant terms, the log-likelihood function of the observed data is
\[
\ell(r, \sigma^2) = - \frac{n}{2} \log(\sigma^2) - \frac{1}{2\sigma^2} \sum_{k=1}^n \frac{\left( X_k - M_k/r \right)^2}{T_k}.
\]
To Estimate $r$, we expand the summation of second term and have 
\[
Q(r) = \sum_{k=1}^n \left( \frac{X_k^2}{T_k} - \frac{2X_k M_k}{r T_k} + \frac{M_k^2}{r^2 T_k} \right)
= A - \frac{2B}{r} + \frac{C}{r^2},
\]
where \( A = \sum X_k^2/T_k \), \( B = \sum X_k M_k/T_k \), and \( C = \sum M_k^2/T_k \). Taking the derivative with respect to \( r \) and setting it to zero gives:
\begin{equation}\label{normal-mle-r}
\frac{dQ}{dr} = \frac{2B}{r^2} - \frac{2C}{r^3} = 0 \quad \Rightarrow \quad \hat{r} = \frac{C}{B} = \frac{\sum M_k^2/T_k}{\sum X_k M_k/T_k}.
\end{equation}
Then, substituting \( \hat{r} \) back into the likelihood, the MLE for \( \sigma^2 \) is obtained by maximizing
\[
\ell(\sigma^2) = -\frac{n}{2} \log(\sigma^2) - \frac{1}{2\sigma^2} \sum_{k=1}^n \frac{\left( X_k - M_k/\hat{r} \right)^2}{T_k},
\]
which yields
\begin{equation}\label{normal-mle-sigma}
\hat{\sigma}^2 = \frac{1}{n} \sum_{k=1}^n \frac{\left( X_k - M_k/\hat{r}\right)^2}{T_k}.
\end{equation}
